---
title: "Untitled"
author: "Junhua Yang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document:
    highlight: "monochrome"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "  ", prompt=TRUE, warning = FALSE, 
                      echo=TRUE, message = FALSE, include=TRUE)
options(max.print=5000)
```

# Load data
```{r, echo=FALSE, include=FALSE}
load("C:/Users/jyz7278/Box Sync/ASCO/Cervical Rad Hyst/NEJM/Data/cer1.3.5.RData")
# load("C:/Users/mnk1805/Box Sync/ASCO/Cervical Rad Hyst/NEJM/Data/cer1.3.5.RData")
cer1 <- as.data.frame(cer1.3.5)
dim(cer1) #1893
library(dplyr)
library(magrittr)
library(ggplot2)
library(tableone)
library(car)
library(coin)
library(knitr)
library(mice)
library(reshape2)
library(survival)
library(survminer)
library(KMsurv)
library(survRM2)
library(MatchIt)
library(gridExtra)
library(cobalt)
library(readxl)

# library(emmeans)

vars <- c("fu","died", "group", "rad_hys_extent", "radchemo", "postop_trt", 
          "tumor_size", "TUMOR_SIZE", "LNcount", "i_margin", "i_LNpos", 
          "i_grade", "LVSI", "histology",  "i_hospvol_cat2", "hospvol2", "i_CDCC", 
          "age", "newrace", "i_insure", "income", "type", "YEAR_OF_DIAGNOSIS", "stage_mgh")
sapply(cer1[vars], function(x)sum(is.na(x))) #21 missing in LNcount

# Change "Minimal Invasive" to "MIS"
levels(cer1$group) <- c("Open", "MIS")


```

# Death event counts
```{r}

table(cer1$died, cer1$group) %>% addmargins()  #91 events
     
with(subset(cer1, cer1$stagefigo=="IB1"), table(died, group)) %>% addmargins  #previously 87 events

with(subset(cer1, cer1$YEAR_OF_DIAGNOSIS!="2013"), table(died, group)) %>% addmargins  #75 events 2010-2012

```



# Import imputed data from Stata
```{r, include=FALSE, echo=FALSE}
# impframe <- read_excel(
#   "C:/Users/mnk1805/Box Sync/ASCO/Cervical Rad Hyst/NEJM/Data/cer4_imputed_062718.xlsx",
#   sheet="Sheet1", na="")
impframe <- read_excel(
  "C:/Users/jyz7278/Box Sync/ASCO/Cervical Rad Hyst/NEJM/Data/cer4_imputed_062718.xlsx",
  sheet="Sheet1", na="")
impframe <- as.data.frame(impframe)
names(impframe)
colnames(impframe)[1] <- ".imp"
colnames(impframe)[2] <- ".id"

dim(impframe)
sapply(impframe, function(x)sum(is.na(x))) 
table(impframe$itumor_size2)

# drop radchemo since it's not imputed
impframe2 <- within(impframe, rm("radchemo", "tumor_size_imp"))
str(impframe2)

#convert vars to factors#
# names <- c(".imp", ".id", "group", "histo", "iLVSI", "rad_hys_extent", "i_hospvol_cat2", 
#            "income", "i_CDCC", "newrace", "i_insure", "ii_margin", "ipostop_trt", 
#            "ii_LNpos", "ii_grade", "itumor_size2", "stage_mgh")
names <- c(".imp", ".id", "group", "rad_hys_extent", "i_hospvol_cat2", 
           "histology", "i_CDCC", "newrace", "i_insure", "type", "income", 
           "YEAR_OF_DIAGNOSIS", "stage_mgh", "ii_margin", 
           "ipostop_trt", "ii_LNpos", "ii_grade", "iLVSI", "itumor_size2")
impframe2[,names] <- lapply(impframe2[, names] , factor)
str(impframe2)

levels(impframe2$itumor_size2) <- c("<2cm", ">=2cm")
levels(impframe2$ipostop_trt) <- c("No", "Yes")
levels(impframe2$iLVSI) <- c("No", "Yes")
impframe2$i_insure <- relevel(impframe2$i_insure, ref="Private")
impframe2$group <- relevel(impframe2$group, ref="Open")
str(impframe2)

# check stata imputation
sapply(impframe2, function(x) summary(x)) # alomost the same as imp in R

imp.data <- impframe2
class(imp.data)

```

## import imputed data including imp=0 #
```{r, include=FALSE, echo=FALSE}

library(readxl)
# impframeall <- read_excel(
#   "C:/Users/mnk1805/Box Sync/ASCO/Cervical Rad Hyst/NEJM/Data/cer4_imputed_all_062718.xlsx",
#   sheet="Sheet1", na="")
impframeall <- read_excel(
  "C:/Users/jyz7278/Box Sync/ASCO/Cervical Rad Hyst/NEJM/Data/cer4_imputed_all_062718.xlsx",
  sheet="Sheet1", na="")
impframeall <- as.data.frame(impframeall)
names(impframeall)
colnames(impframeall)[1] <- ".imp"
colnames(impframeall)[2] <- ".id"
dim(impframeall) #27071 = 2461*11


# impframeall2 <- impframeall[c(1,2,3,4,5,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,
#                               22,23,24,25,26,27,29)]
# str(impframeall2)

# impframeall <- impframeall2

# names <- c(".imp", ".id", "group", "histo", "iLVSI", "rad_hys_extent", "i_hospvol_cat2", 
#            "income", "i_CDCC", "newrace", "i_insure", "ii_margin", "ipostop_trt", 
#            "ii_LNpos", "ii_grade", "itumor_size2", "stagefigo")
names <- c(".imp", ".id", "group", "rad_hys_extent", "i_hospvol_cat2", 
           "histology", "i_CDCC", "newrace", "i_insure", "type", "income", 
           "YEAR_OF_DIAGNOSIS", "stage_mgh", "ii_margin", 
           "ipostop_trt", "ii_LNpos", "ii_grade", "iLVSI", "itumor_size2")

impframeall[,names] <- lapply(impframeall[,names] , factor)
str(impframeall)

levels(impframe2$itumor_size2) <- c("<2cm", ">=2cm")
levels(impframeall$ipostop_trt) <- c("No", "Yes")
levels(impframeall$iLVSI) <- c("No", "Yes")
impframeall$i_insure <- relevel(impframeall$i_insure, ref="Private")
impframeall$group <- relevel(impframeall$group, ref="Open")


# impframeall$tumor_postop <- interaction(impframeall$itumor_size2,impframeall$ipostop_trt)

sapply(impframeall, function(x)sum(is.na(x)))

imp.data.all <- as.mids(impframeall)


```


# Fitting model for Imputed data

## Fit final model

```{r, include=FALSE, echo=FALSE}

# Formula for the final model, based on models selection
# frm.final <- as.formula(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
#                           ii_grade + age + newrace + stage_mgh + i_insure)

frm.final <- as.formula(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                          ii_grade + age + newrace + i_insure)

# Fit final model in the imputed data set
fit1 <- vector("list", nlevels(imp.data$.imp))
for (i in 1:10){
  sub <- subset(imp.data, imp.data$.imp == i)
  # fit1[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
  #                      ii_grade + age + newrace + stage_mgh + i_insure, data=sub)
    fit1[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                       ii_grade + age + newrace + i_insure, data=sub)
}

fit1.mira <- as.mira(fit1)
summary(pool(fit1.mira, method="smallsample")) 

pool.fit1 <- as.data.frame(summary(pool(fit1.mira)))  
names(pool.fit1)
colnames(pool.fit1)[5]<-"pvalue"
colnames(pool.fit1)[6]<-"lo"
colnames(pool.fit1)[7]<-"hi"

pool.fit1
```

## Get p-value for i_insure (insrance type)
```{r, include=FALSE, echo=FALSE}

# Fit final model in the imputed data set
fit1 <- vector("list", nlevels(imp.data$.imp))
for (i in 1:10){
  sub <- subset(imp.data, imp.data$.imp == i)
  # fit1[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
  #                      ii_grade + age + newrace + stage_mgh + i_insure, data=sub)
  fit1[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                       ii_grade + age + newrace + i_insure, data=sub)
}

fit1.mira <- as.mira(fit1)
summary(pool(fit1.mira, method="smallsample"))

pool.fit1 <- as.data.frame(summary(pool(fit1.mira)))  
names(pool.fit1)
colnames(pool.fit1)[5]<-"pvalue"
colnames(pool.fit1)[6]<-"lo"
colnames(pool.fit1)[7]<-"hi"

# Remove insurance
fit.noins <- vector("list", nlevels(imp.data$.imp))
for (i in 1:10){
  sub <- subset(imp.data, imp.data$.imp == i)
  # fit.noins[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
  #                               ii_grade + age + newrace + stage_mgh, data=sub)
    fit.noins[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                                ii_grade + age + newrace, data=sub)
}

fit.nonins.mira <- as.mira(fit.noins)
summary(pool(fit.nonins.mira, method="smallsample")) 

pool.fit.noins <- as.data.frame(summary(pool(fit.nonins.mira)))  
names(pool.fit.noins)
colnames(pool.fit.noins)[5]<-"pvalue"
colnames(pool.fit.noins)[6]<-"lo"
colnames(pool.fit.noins)[7]<-"hi"

# Compare fit1 vs. fit.noins (i.e. get Wald test for insurance)
poolcomp.ins <- pool.compare(fit1.mira, fit.nonins.mira, method="Wald")
pval.ins <- poolcomp.ins$pvalue
format.pval(pval.ins)

```

# Get pvalue for newrace
```{r, include=FALSE, echo=FALSE}

# Fit final model in the imputed data set
fit1 <- vector("list", nlevels(imp.data$.imp))
for (i in 1:10){
  sub <- subset(imp.data, imp.data$.imp == i)
  # fit1[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
  #                      ii_grade + age + newrace + stage_mgh + i_insure, data=sub)
  fit1[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                       ii_grade + age + newrace + i_insure, data=sub)
}

fit1.mira <- as.mira(fit1)
summary(pool(fit1.mira, method="smallsample"))

pool.fit1 <- as.data.frame(summary(pool(fit1.mira)))  
names(pool.fit1)
colnames(pool.fit1)[5]<-"pvalue"
colnames(pool.fit1)[6]<-"lo"
colnames(pool.fit1)[7]<-"hi"

# Remove newrace
fit.norace <- vector("list", nlevels(imp.data$.imp))
for (i in 1:10){
  sub <- subset(imp.data, imp.data$.imp == i)
  # fit.noins[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
  #                               ii_grade + age + newrace + stage_mgh, data=sub)
    fit.norace[[i]] <- coxph(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                                ii_grade + age + i_insure, data=sub)
}

fit.norace.mira <- as.mira(fit.norace)
summary(pool(fit.norace.mira, method="smallsample")) 

pool.fit.norace <- as.data.frame(summary(pool(fit.norace.mira)))  
names(pool.fit.norace)
colnames(pool.fit.norace)[5]<-"pvalue"
colnames(pool.fit.norace)[6]<-"lo"
colnames(pool.fit.norace)[7]<-"hi"

# Compare fit1 vs. fit.noins (i.e. get Wald test for insurance)
poolcomp.race <- pool.compare(fit1.mira, fit.norace.mira, method="Wald")
pval.race <- poolcomp.race$pvalue
format.pval(pval.race)
```



# Propensity Score Matched Model
```{r, include=FALSE, echo=FALSE}

par(ask=F)

varexcl <- c(".imp", ".id", "fu", "died", "radchemo", "ch", "tumor_size_imp", "group") 
vnames <- names(imp.data)[!(names(imp.data) %in% varexcl)]

frm.ps <- paste("num ~ ", paste(vnames, collapse=" + ")) %>% as.formula

# Make formulas for insurance and race, to get multi-df pvalues
frm.final.wins <- as.formula(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                          ii_grade + age + newrace + i_insure)
frm.final.woins <- as.formula(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                          ii_grade + age + newrace )

frm.final.wrace <- as.formula(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                          ii_grade + age + i_insure + newrace)
frm.final.worace <- as.formula(Surv(fu, died) ~ group + ipostop_trt + itumor_size2 + ii_LNpos + 
                          ii_grade + age + i_insure )


```


```{r, include=FALSE, echo=FALSE}
M <- nlevels(imp.data$.imp)
fit.wins <- vector("list", M)
fit.woins <- vector("list", M)
fit.wrace <- vector("list", M)
fit.worace <- vector("list", M)
fit.match1 <- vector("list", M)
loveplot <- vector("list", M)

set.seed(62818)
for (i in 1:M){
  m.out <- matchit(frm.ps, caliper=0.5, data=imp.data[imp.data$.imp == i,])
  matcheddata <- match.data(m.out)
  # matcheddata$died %>% table
  fit.wins[[i]] <-   coxph(frm.final.wins, data=matcheddata)
  fit.woins[[i]] <-  coxph(frm.final.woins, data=matcheddata)
  fit.wrace[[i]] <-  coxph(frm.final.wrace, data=matcheddata)
  fit.worace[[i]] <- coxph(frm.final.worace, data=matcheddata)
  fit.match1[[i]] <- fit.wins[[i]] # final model, just named more intuitively
  
  bal <- bal.tab(m.out)
  loveplot[[i]] <- love.plot(bal, abs=TRUE, line=TRUE, var.order = "adjusted")
} 

fit.wins.mira   <- as.mira(fit.wins)
fit.woins.mira  <- as.mira(fit.woins)
fit.wrace.mira  <- as.mira(fit.wrace)
fit.worace.mira <- as.mira(fit.worace)
fit.match1.mira <- as.mira(fit.match1)

fit.list.mira1 <- as.mira(fit.match1)

# Get Wald test for insurance
poolcomp.ins <- pool.compare(fit.wins.mira, fit.woins.mira, method="Wald")
pval.match.ins <- poolcomp.ins$pvalue
format.pval(pval.match.ins)

# Get Wald test for race
poolcomp.race <- pool.compare(fit.wrace.mira, fit.worace.mira, method="Wald")
pval.match.race <- poolcomp.race$pvalue
format.pval(pval.match.race)
```


```{r, include=FALSE, echo=FALSE}
# check love plot for matched dataset
loveplot[[1]]
loveplot[[2]]
loveplot[[3]]
loveplot[[4]]
loveplot[[5]]
loveplot[[6]]
loveplot[[7]]
loveplot[[8]]
loveplot[[9]]
loveplot[[10]]

# for (i in 1:10){
#   print(loveplot[[i]])
# }

# with caliper=0.6, event=154, absolute mean difference a little bit >0.1 for year of diagnosis
# with caliper=0.5, event=147, all vars well balanced

# Absolute mean differences with a threshold of .1 
# https://cran.r-project.org/web/packages/cobalt/vignettes/cobalt_A0_basic_use.html


```
# Results
## Final imputed model

Results from the final imputed model. The ovarall Wald test pvalue for insurance is `r format.pval(pval.ins, digits=4)` and for race is `r format.pval(pval.race, digits=4)`.


```{r}
data.frame(values=row.names(pool.fit1),
           HR = pool.fit1$est %>% exp,
           LL = pool.fit1$lo %>% exp,
           UL = pool.fit1$hi %>% exp,
           pvalue = pool.fit1$pvalue %>% format.pval(digits=4, eps=.0001))

```

## Propensity score matched results

Results from the final imputed model with propensity score matching. The ovarall Wald test pvalue for insurance is `r format.pval(pval.match.ins, digits=4)` and for race is `r format.pval(pval.match.race, digits=4)`.


```{r, include=FALSE}
pool.match1 <- as.data.frame(summary(pool(fit.list.mira1)))  
names(pool.match1)
colnames(pool.match1)[5]<-"pvalue"
colnames(pool.match1)[6]<-"lo"
colnames(pool.match1)[7]<-"hi"
```

```{r}
data.frame(values=row.names(pool.match1),
           HR = pool.match1$est %>% exp,
           LL = pool.match1$lo %>% exp,
           UL = pool.match1$hi %>% exp,
           pvalue = pool.match1$pvalue %>% format.pval(digits=4, eps=.0001))


```

